### 2023-03-24 resilience.tex
up

\begin{theorem}\label{k-down-up}
Let $\mathscr{S}=(S,\rightarrow, \leq)$ be a completion-post-effective $\omega^2$-WSTS with strong compatibility and the predbasis hypothesis, and two finite sets: $I_{\Bad}$ and $Min_{\Safe}$.
The  $k$-resilience problem (kRP) is decidable for $k \geq K$. \textcolor{red}{CONJECTURE for now}
 \end{theorem}

>>>>

\begin{theorem}\label{k-down-up}
Let $\mathscr{S}=(S,\rightarrow, \leq)$ be a completion-post-effective $\omega^2$-WSTS with strong compatibility and the predbasis hypothesis, and two finite sets: $\Bad$ and $\Safe$.
The  $k$-resilience problem (kRP) is decidable for $k \geq K$. \textcolor{red}{CONJECTURE for now}
 \end{theorem}
